\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{// All comments are NOT created equal}

### 2015-05-16 paper/paper.tex
adding section about distance keeping

\subsection{a}

\subsection{b}

\subsection{c}
\newpage
\section{Towards an Optimal Scanning Algorithm}
\label{sec:optimalScanningAlgorithm}

@@

Using this logic, the robot may run into issues

\subsection{Fixing holes}
\ednote{more sensors}

@@

\section{Future Work and Possible Extensions}

>>>>

\subsection{ROS}

\subsection{Octomap}
\ednote{DENIS}

\subsection{Robot Overview}
\ednote{can move and has a pan tilt unit and a sensor}

\newpage
\section{Towards an Optimal Scanning Algorithm}
\label{sec:optimalScanningAlgorithm}

@@

Using this logic, the robot may run into issues because it does not have sensors above, below, or behind. This will not be covered in this paper but we will discuss this in \autoref{sec:limitations} and elaborate how it could be done in \autoref{sec:future}. Apart from running into objects, the robot can also fail to scan all areas due to the fact that we use the closest point in our field of vision to determine where we should be (see \autoref{fig:codeDistance}). In the case of spikes some areas may thus remain unscanned. The latter problem will be discussed in the next subsection.\\

\subsection{Fixing holes}
\ednote{more sensors or looking left and right}

\section{Limitations}
\label{sec:limitations}
\subsection{Obstacle avoidance}
\ednote{limitation ->  query octomap around us}
\ednote{disadvantage dynamic object like fish}

@@

\section{Future Work and Possible Extensions}
\label{sec:future}
